---
title: "Schedule"
slug: schedule
summary: "Schedule of the Gov 50 semester with readings and corresponding dates."
toc: false
sidebar: false
page-layout: full
---
           
```{r packages-data, include=FALSE} 
library(tidyverse)
library(knitr)
library(kableExtra)
library(lubridate)
library(glue)

schedule <- read_csv("class_data/schedule.csv", show_col_types = FALSE) 
```
        

Below is the schedule for the semester. You should:
   
- complete readings before class;
- submit answers to warmup questions on Canvas by 1 hour before class; and
- turn in homework assignments, printed and in-person to your TF/CA, by the beginning of class.
                

The readings refer to following texts:   

- **ROS**: [*Regression and Other Stories*](https://avehtari.github.io/ROS-Examples/) by Andrew Gelman, Jennifer Hill, & Aki Vehtari
- **TE**: [*The Effect: An Introduction to Research Design and Causality*](https://moderndive.com/index.html) by Nick Huntington-Klein


::: callout-important
#### This schedule is subject to change

  Ideally, we will be able to cover all of this content in the semester, but given that there may be unforeseen issues (e.g., university closures or sickness) this schedule is subject to change. However, if there are changes this page will be updated and there will be an announcement made on [Ed Discussion Board](https://edstem.org/us/courses/101357/discussion).

:::
 
 
```{r build-table, echo=FALSE, results="asis"}
schedule <- schedule %>%  
    # mutate(var_title = ifelse(!is.na(title),
    #                           glue('<span class="content-title">{title}</span>'),
    #                           glue(""))) %>%
    mutate(col_module = paste0("Module ",module, ": ", title)) %>%
    mutate(var_reading = ifelse(!is.na(reading),
                              glue('<span class="content-reading">{reading}</span>'),
                              glue(""))) %>%
    mutate(col_date = glue('<strong>{date}</strong>')) %>%
    #mutate(col_title = glue('{var_module}{var_title}')) %>%
    mutate(col_reading = var_reading) %>%
  select(Module = col_module, Date = col_date, Title = title, Reading = col_reading)

schedule$Title <- c(rep(c('<span class="content-reading">First Class</span>', '<span class="content-reading">Second Class</span>'), 12),schedule$Title[25:26])

module_count <- schedule |> count(Module)
module_index <- module_count |> pull(n) |> set_names(module_count$Module)

module_index <- module_index[-14]

module_index[13] <- 2

module_index <- module_index |> set_names(c(names(module_index)[1:12],"Reading and Finals Weeks"))

module_index <- module_index[c(4:12,1:3,13)]

 
tbl <- schedule |>
  select(-Module) |>
  kbl(escap = FALSE, align = "lll", table.attr = 'class="schedule-table"') |>
  kable_styling() |>
  column_spec(1, width = "20%", extra_css = "padding-right: 20px;") |>  
  column_spec(2, width = "50%") |>  
  column_spec(3, width = "30%") |>
  pack_rows(index = module_index,
              label_row_css = "border-bottom: 2px solid #000000;")
  

  cat(tbl)
```
  
